Title

### 2022-11-03 Manuscript/Manuscript.Rmd
results and plot
Quick check from Nacho

1. Understanding the mechanisms driving community stability and whether this stability should be related to the stability of ecosystem functions is important for predicting changes in both community structure and ecosystem function. While community stability can be influenced by species richness and asynchrony of species,  the relation with the stability of ecosystem functioning is less explored, and specially for functions involving several trophic levels such as plant pollination.

2. Using a 5-year time dataset in Mediterranean woodland patches, we assessed the effect of the richness and asynchrony pollinators as drivers of the stability of visitation rate and the relationship between the stability of visitation rate and the stability of the plants reproductive success. In addition, we analyzed whether the year together with richness and visitation rate affected the proportion of fruits and the number of seeds.

3. The stability of visitation rate is affected by the asynchrony of species while richness shows different responses depending on the plant species. As for the stability of the plant reproductive success, we found no relationship between the stability of the proportion of fruits and the number of seeds and the stability of the visitation rate. When we analyzed year as a factor, although fruit proportion was saturated, we observed that the effect of richness on fruit proportion depends on the year. This relationship is not found with seed number.

@@

Our study was conducted in the southwest of the Iberian Peninsula (Huelva and Seville - Spain). We selected 13 sites in Mediterranean shrub ecosystems that ranged from sites with little to no disturbances to more modified ones with crops and urban areas nearby. These sites had similarity in plant community composition and some of most abundance plant species provide nectar and pollen that attract flower visitors. Each site was surveyed at least 7 times per year during the flowering season from 2015 to 2019 (from March to June). Within each site, we selected 3-4 individuals belonging to 3-9 plant species (mean  ± standard error: 5.92  ± 0.54 plant species per site). All the floral visitors (from now on referred to as pollinators) that contacted with their flowers  were registered over 5 minutes. Only pollinators that could not be identified in the field were captured, stored, and identified to species level in the laboratory. For each plant individual, we counted the total number of flowers and at the end of the season, we recorded the number of fruit and the seeds per fruit.
For each site and year, we calculated the visitation rate of pollinators as the number of visits divided by the number of flowers, pollinator richness, the fruit set as the proportion of fruit, and the seed set as number of seed for each plant individual sampled per site.

## Stability
For the study of stability, we used 5 plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) because of they were present in at least 5 sites during the 5 years. The stability of visitation rate was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot. To examine the role of richness and synchrony of pollinator species as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot during the five years. To synchrony, we used the Loreau and de Mazancourt index (2008), the weighted form of the synchrony index (Gross et al., 2014; Blüthgen et al., 2016), and the log of variance ratio (log VR) (Schluter, 1984; Hallett et al., 2014; Lepš et al., 2018). All of them were positively correlation in each plant species, therefore, data for synchrony assessed by Loreau and de Mazancourt index are presented and included in our further analyses. This synchrony measurement varies from zero, when fluctuations are perfectly asynchronous, to one, when fluctuations are perfectly synchronous. Finally, we express asynchrony as 1-Loreau and de Mazancourt’s index of synchrony.
We also calculated the stability of fruit proportion and of the seed number for each plant species in each plot.

@@

Stability of fruit proportion varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged 1.28 to 55.86 (7.018 ± 1.441).
When we analyzed whether the stability of the visitation rate affected the stability of the plant reproductive success, we found no relationship between this and the stability of the fruit proportion (Estimate: 4.692; std. error: 4.545), and neither with the stability of the number of seeds (Estimate: 0.859; std. error: 1.825).

>>>>

1. Understanding the mechanisms driving community stability and whether this stability should be related to the stability of ecosystem functions is important for predicting the resilience of communities to changes in biodiversity. While community stability can be influenced by species richness and asynchrony of species,  the relation with the stability of ecosystem functioning provided by this community is less explored, and specially for functions involving several trophic levels such as plant pollination.

2. Using a 5-year dataset across 16 Mediterranean woodland patches, we assessed the effect of the richness and asynchrony of pollinators as drivers of the stability of plant's visitation rate and its relationship between the stability of visitation rate and the stability of the plants reproductive success. [In addition, we analyzed whether the year together with richness and visitation rate affected the proportion of fruits and the number of seeds.](esto pensamos como ponerlo con los results finales)

3. The stability of plant's visitation rate is mainly affected by the asynchrony of pollinator species abundances while pollinator richness shows contrasting responses depending on the plant species. As for the stability of the plant reproductive success, we found no relationship between the stability of fruits or seed set and the stability of the visitation rate. This is because for most years, visitation rates are high enough to prevent pollen limitation, but interestingly, in bad[?]() years the effect of pollinator richness on fruit proportion becomes important.

@@

Our study was conducted in the southwest of the Iberian Peninsula (Huelva and Seville - Spain). We selected 13 sites in Mediterranean shrub ecosystems that ranged from sites with little to no disturbances to more modified ones with crops and urban areas nearby. These sites had similarity in plant community composition and some of most abundance plant species provide nectar and pollen that attract flower visitors. Each site was surveyed at least 7 times per year during the flowering season from 2015 to 2019 (from March to June). Within each site, we selected 3-4 individuals belonging to 3-9 plant species (mean  ± standard error: 5.92  ± 0.54 plant species per site). All the floral visitors (from now on referred to as pollinators) that contacted with their flowers  were registered in visits per flower and minutes by performing timed focal observations to the selected individuals. Only pollinators that could not be identified in the field were captured, stored, and identified to species level in the laboratory. For each plant individual, we counted the total number of flowers and at the end of the season, we recorded the number of fruit and the seeds per fruit.
For each site and year, we calculated the visitation rate of pollinators as the number of visits divided by the number of flowers, pollinator richness, the fruit set as the proportion of fruit, and the seed set as number of seed for each plant individual sampled per site.

## Stability
For the study of stability, we used 5 plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) because of they were recorded in at least 5 sites during the 5 years. The stability of visitation rate was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following (REF). To examine the role of richness and synchrony of pollinator species as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot during the five years. For synchrony, we used the Loreau and de Mazancourt index (2008), the weighted form of the synchrony index (Gross et al., 2014; Blüthgen et al., 2016), and the log of variance ratio (log VR) (Schluter, 1984; Hallett et al., 2014; Lepš et al., 2018). All of them were positively correlated within each plant species, therefore, data for synchrony assessed by Loreau and de Mazancourt index are presented and included in our further analyses. This synchrony measurement varies from zero, when fluctuations are perfectly asynchronous, to one, when fluctuations are perfectly synchronous. Finally, we express asynchrony as 1-Loreau and de Mazancourt’s index of synchrony.
We also calculated the stability of fruit proportion and of the seed number for each plant species in each plot.

@@

Stability of fruit proportion varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged 1.28 to 55.86 (7.018 ± 1.441).
When we analyzed whether the stability of the visitation rate affected the stability of the plant reproductive success, we found no relationship between this and the stability of the fruit proportion (Estimate: 4.692; std. error: 4.545) (Fig 2A), and neither with the stability of the number of seeds (Estimate: 0.859; std. error: 1.825) (Fig 2B).
